Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-19 Latex/tex/pr.tex
try

To achieve optimum $\boldsymbol{Y}$ heuristic algorithm and Mosek is applied. The details of heuristic algorithm is written in \textbf{Algorithm} \eqref{alg3}. In this algorithm, firstly we sort slices and DCs according to their sum-weighted of their requirements. Secondly, we start mapping from the most needs slices to the DC which has the most physical resources. After mapping DCs to slices, if some slices are not admitted, we start admitting residual slices to more than one DCs. At the end, if DC with the lowest physical resources is free and can served instead of DC with highest physical resource, the slices remapped to new DC with lowest physical resource since it has lowest power consumption.  

@@

  Noise power & -174dBm\\

@@

  Bandwidth & 10MHZ \\

@@

 Maxmimun transmit Power & 23dBm \\

@@

  Minimum data rate &  1Mbits/sec \\ [1ex] 

@@

In fig. \ref{fig:f1}, the ratio of admitted slices that connected to just one DC is demonstrated for two different number of DCs with different number of slices (the parameters for simulation listed in table \ref{table:1}). When number of DCs are low, proposed method and optimal method have approximately same ratio of admitted slices.   

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=\linewidth]{f2}
  \caption{Normalized resource consumption vs. Number of slices}
  \label{fig:f1}
\end{figure} 
\bibliographystyle{ieeetr}
\bibliography{ref}
\end{document}

>>>>

To achieve optimum $\boldsymbol{Y}$ heuristic algorithm and Mosek is applied. The details of heuristic algorithm is written in \textbf{Algorithm} \eqref{alg3}. In this algorithm, firstly we sort slices and DCs according to their sum-weighted of their requirements. Secondly, we start mapping from the most needed slices to the DC with the most physical resources. After mapping DCs to slices, if some slices are not admitted, we start admitting residual slices to more than one DCs. At the end, if DC with the lowest physical resources is free and can served instead of DC with highest physical resource, the slices remapped to new DC with lowest physical resource since it has lowest power consumption.  

@@

  Mean of CPU for DCs & 25.6GHz\\

@@

  Mean of RAM for DCs & 128G\\

@@

 Mean of Memory for DCs & 10T \\

@@

   Mean of CPU for Slices & 3.2GHz\\
  Mean of RAM for Slices & 16G\\
 Mean of Memory for Slices & 1T \\ [1ex] 

@@

In Fig. \ref{fig:f1}, the ratio of admitted slices is demonstrated for two different number of DCs with different number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}). In this simulation, it is assumed that each slice can be served by just one DC and it is not admitted by more than one DC. Proposed method is based on Algorithm \ref{alg3} and optimal method is done by MOSEK toolbox. 
 \caption {Simulation Parameter} \label{table:2} 
   $w_C$ & 320\\
  $w_R$  & 64\\
 $w_M$  & 1 \\ [1ex] 
When we have two DCs, proposed method and optimal method have approximately same ratio of admitted slices. But by increasing the number of DCs to five, performance of proposed method reduced.

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=\linewidth]{f2}
  \caption{Normalized resource consumption vs. Number of slices}
  \label{fig:f2}
\end{figure} 
\bibliographystyle{ieeetr}
\bibliography{ref}
\end{document}
